### 2023-09-04 paper/sec-pheno.tex
results section

Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 (top panels)
and with PDF4LHC21 (bottom panels),
compared with the results obtained from
the fits including the FPF structure function projections.
%
For the latter, we display the variants based only on statistical uncertainties and that
which includes also systematic errors.
%
The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
%
See~\cite{NNPDF:2021njg} for the calculational settings.
%
From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
%
The corresponding comparison at the level of differential distributions
are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
%
As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
we only indicate the relative PDF uncertainty in each fit, with central values
assumed to be the same by construction.

@@

Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated} and~\ref{fig:NNPDF40_pheno_differential}
quantifies the potential of neutrino structure function measurements at the LHC
to improve theoretical predictions for electroweak and high-scale processes at the HL-LHC.
%
Concerning first the fiducial integrated cross-sections, a reduction of PDF
uncertainties is observed for all processes,
including for $W^+$ production relevant for $m_W$ measurements, and its specific  magnitude depends
on the underlying scattering reaction.
%
This finding also applies for Higgs associated production with vector bosons and in vector-boson-scattering,
with for example
PDF uncertainties in $hW^+$ reduced by up to a factor two thanks to the FPF measurements.
%
Similar remarks apply to the diboson cross-sections, with in this case the largest
improvement observed for $ZW^+$ channel.
%
Reassuringly, LHC predictions based on the fits with FPF pseudo-data are stable
upon the inclusion of the experimental systematic uncertainties in the fit.

In the case of the differential cross-sections shown in Fig.~\ref{fig:NNPDF40_pheno_differential},
we observe how the impact of the FPF structure functions on LHC observables depends
on the hard-scattering scale.
%
For instance, searches for heavy-resonances in the high-mass tail of the Drell-Yan
distributions are going to be improved by FPF data.
%
The same applies for diboson prediction, and in the case of the $ZW^+$ channel we observe
an improvement spatially in the low $p_{T,\ell\bar{\ell}}$ region.
%
For the Higgs production processes, the PDF uncertainty in the theory predictions is relatively
stable as a function of the rapidity.
%
The effects of accounting for systematic uncertainties in the fit are somewhat more visible
here as compared to the inclusive cross-sections, indicating that they affect mostly
the tails, rather than the bulk, of the distributions, and in particular the large-$x$
behaviour of the PDFs.

The studies presented in this section provide only a first glimpse of the potential
of neutrino DIS measurements at the LHC to inform predictions for high-$p_T$ processes.

>>>>

Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 (top panels)
and with PDF4LHC21 (bottom panels),
compared with the results obtained from
the corresponding fits including the FPF structure function projections.
%
For the fits with FPF data we display the variants where the covariance matrix
consists only of statistical errors (``\_FPF'') and where also
systematic errors are accounted for (``\_FPF$^*$'').
%
For the baseline
predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
%
The central values are set to be the same as in the baseline calculation in all cases.
%
From top to bottom, we show inclusive Drell-Yan production in the $Z$, $W^+$, and $W^-$
channels, Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production in the $W^+W^-$, $W^+Z$, and $W^-Z$ final-states.
%
The corresponding comparisons at the level of differential distributions
are shown in Figs.~\ref{fig:NNPDF40_pheno_differential} and~\ref{fig:PDF4LHC21_pheno_differential}
for NNPDF4.0 and PDF4LHC21 respectively.
%
As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
we only indicate the relative PDF uncertainty in each fit, with central values
assumed to be unchanged.

@@

Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated}--\ref{fig:PDF4LHC21_pheno_differential}
confirms the potential of LHC neutrino structure function measurements
to improve theoretical predictions for Higgs, electroweak and high-mass
processes at the HL-LHC.
%
In general, qualitative consistency between the results based on NNPDF4.0
and on PDF4LHC21 is found, as was already the case at the PDF level.
%
As  compared to the limiting scenario where only statistical uncertainties
are taken into account, the reduction of PDF errors in the LHC cross-sections
obtained thanks for the FPF structure functions becomes less marked,
but still visible for most of the processes under consideration,
upon the inclusion of systematic uncertainties in the fit covariance matrix.

Concerning the fiducial integrated cross-sections, a decrease in PDF
uncertainties is observed for all processes,
including for single gauge boson production relevant for core
HL-LHC analyses such as the $m_W$ and $\sin^2\theta_W$ measurements.
%
The specific improvement in precision depends
on the underlying scattering reaction as well as on the range
of $x$ and $Q^2$ covered by each process.
%
In the case of  Higgs associated production with vector bosons and in vector-boson
scattering,
driven by the quark-antiquark and quark-quark initial states respectively,
one observes that PDF uncertainties can  be reduced
by up to a factor two thanks to the FPF measurements, for instance
in the case of the $hW^+$ and $hW^-$ cross-sections,
in the most optimistic scenario in which systematic uncertainties
are neglected.
%
Likewise for the diboson cross-sections, with in this case the largest
improvement observed for the $ZW^+$  and  $ZW^-$ final states, with a reduction
of up to $\sim 40\%$ in the PDF uncertainties.

In the case of the differential cross-sections displayed in Figs.~\ref{fig:NNPDF40_pheno_differential}
and~\ref{fig:PDF4LHC21_pheno_differential},
we observe how the impact of the FPF structure functions on LHC observables depends
on the hard-scattering scale.
%
For instance, searches for heavy resonances in the high-mass tail of the Drell-Yan
distributions could be improved by the addition of the FPF data.
%
Similar considerations apply for diboson prediction, and in the case of the $ZW^{\pm}$ channel we observe
an improvement specially in the low $p_{T,\ell\bar{\ell}}$ region which
represents the bulk of the fiducial cross-sections.
%
For the Higgs production processes, the PDF uncertainty in the theory predictions is relatively
stable as a function of the rapidity.
%
The effects of accounting for systematic uncertainties in the fit covariance
matrix are somewhat more visible here as compared to the inclusive cross-sections,
indicating that they affect mostly
the tails, rather than the bulk, of the distributions, and in particular the large-$x$
behaviour of the PDFs.
%
This observation emphasizes the importance of reducing systematic errors
in the FPF measurements in order to enhance the cross-talk with HL-LHC analyses.

### 2023-09-04 paper/sec-results.tex
results section

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|c|c|c}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & \multirow{2}{*}{Baseline}
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  &  &  2.256  &  2.242   & 2.215   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & & 2.360    &   2.332  & 2.311  \\
  $\la \chi^2\ra_{\rm rep}$
  & &   1.194   &    1.187    & 1.169  \\
  \midrule
  \multirow{8}{*}{$\chi^2$}
  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
  & FPF (total)                 &  -  &       &      \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to the variants including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
  $\chi^2$ for datasets grouped by process.
  %
  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{plots/lumi-FPFall.pdf}
\caption{Comparison of the PDF luminosities at $\sqrt{s}=14$ TeV
  as a function of the final-state invariant mass $m_X$ between
  the baseline NNPDF4.0 NNLO determination and its variants which include
  the full set of FPF pseudo-data, see Figs.~\ref{fig:NNPDF40_baseline}
  for the corresponding PDF comparison.
  %
  Results are shown normalised to the central value of the NNPDF4.0 baseline.
  %
  From left to right we show the gluon-gluon, quark-antiquark, and
  quark-quark luminosities.
%
}
\label{fig:nnpdf40_fpf_lumis}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|c|c|c}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & \multirow{2}{*}{Baseline}
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  &  &  2.256  &  2.242   & 2.215   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & & 2.360    &   2.332  & 2.311  \\
  $\la \chi^2\ra_{\rm rep}$
  & &   1.194   &    1.187    & 1.169  \\
  \midrule
  \multirow{8}{*}{$\chi^2$}
  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
  & FPF (total)                 &  -  &   1.192    &   0.919   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to the variants including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
  $\chi^2$ for datasets grouped by process.
  %
  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.99\textwidth]{plots/lumi-FPFall.pdf}
\caption{Comparison of the PDF luminosities evaluated at $\sqrt{s}=14$ TeV
  as a function of the final-state invariant mass $m_X$ between
  the baseline NNPDF4.0 NNLO determination and its variants which include
  the full set of FPF pseudo-data, see Figs.~\ref{fig:NNPDF40_baseline}
  for the corresponding PDF comparison.
  %
  Results are shown normalised to the central value of the NNPDF4.0 baseline.
  %
  From left to right and top to bottom we show the gluon-gluon, quark-antiquark,
  quark-quark, down-antiup, up-antistrange, and strange-antistrange luminosities.
  %
  The bands in the NNPDF4.0 baseline indicate the one-sigma PDF uncertainties.
%
}
\label{fig:nnpdf40_fpf_lumis}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
